### 2024-06-18 doc/Thesis/chapter/020-theory-materials.tex
edit 020 until excl sputtering

%\td{https://en.wikipedia.org/wiki/Thesis}
\ds{what is it? What is it used for? How does it work? What different kinds are there? }
\ds{what? how? why?}
This chapter can be broken down into three sections. 
The first section tries to shine light on the evolution of PV and give some background information on \gls{cigs}.
The middle section reads about material-scientific methods which were used during the practical part of this work. 
The last and third part focuses on the algorithmic, statistical and analytical methods used to optimize and predict material properties.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Photovoltaics}
%\subsection{Problems of current energy supply}
The world wide energy consumption has more than doubled between 1970 and 2015\cite{BP2017} 
and according to recent studies both fossil\cite{BGR2017} and uranium sources\cite{Uran2006} 
will be exhausted within the next 100 years. 
Even though this time period is not exact and highly dependent on detection methods of resources, 
this number is rather small and brings us in \textit{zugzwang} to develop sustainable energy sources. 
One viable option is \gls{pv}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{History of Photovoltaics}
The photoelectric effect was first described in 1839 by french scientist Alexandre 
Edmond \linebreak[4] 
Becquerel\cite{becquerel1839memoire}. %, the father of Henri Becquerel (the person after whom the unit is named).
Another relevant piece in the \gls{pv} jigsaw was brought to light
%discovered
with the discovery of photo conductivity of selenium
by British engineer Willouhgby Smith\cite{Smith1873Selenium}.
In 1876 William Adams and Richard Day\cite{Adams1876Selenium} showed that 
the energy of light can be directly converted into electrical energy by a bar of 
selenium with attached platinum electrodes.
And finally, in 1905 Einstein described the physical background of the photoelectric 
effect with his light quantum theory\cite{einstein1905erzeugung}.
%\todo{https://doi.org/10.1063/1.1716492}
In the late 1950s the first solar cells (with efficiencies around 10 percent\cite{prince1958}) were used in niche applications such as space exploration.  
In 1958 the US American Vanguard I\cite{vanguard2004} and the soviet Sputnik III\cite{sputnik1959} were the first satellites with solar cells.
These "solar batteries" - as they were called then - allowed the transmission system of Vanguard I to be operating for over a year after the chemical battery powered system stopped transmitting after 20 days\cite{vanguard2004}. 
%
Eventually, the interest in photovoltaic and other alternative energy sources 
rose - fuelled by the oil crisis in 1973 - 
and the development of photovoltaic devices for the consumer market was boosted. 
This development lead to a drop in 
average price for \gls{pv} module from \$ 100 per watt in 1975 to \$ 4 per watt in 2007\cite{pagliaro2008flexible}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Photovoltaics Basics}
The process of conversion of photons into voltaic energy can be broken down into two essential steps (both in human made \gls{pv} or in plants): 
the creation of an electron-hole pair and then its separation by the structure of the material\cite{markvart2013principles}.
This means that \gls{pv} cells are basically diodes, which have a low resistance in one direction and a high resistance in the other direction. 
This is often achieved through a p-n junction.
The n-type side has excess electrons and p-type side has excess electron holes. 
If the n- and p-type are of the same basis material, they are called homojunctions (e.g. silicon); if not, heterojunctions e.g. \ch{CdS}/\gls{cigs} and \ch{CdS/CdTe}\cite{breitenstein2013understanding}.
%
The first marketable \gls{pv} were crystalline silicon photovoltaic modules which still 
have the biggest market share in the \gls{pv} segment (including polycrystalline and monocrystalline silicon).
In 2022 
over 88\% of all sold \gls{pv} where made of silicon (including amorphous silicon)\cite{breitenstein2013understanding}.
%
A comprehensive overview on different \gls{pv} technologies can be found in \cite{markvart2013principles}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Copper Indium Gallium Selenide Solar Cell}
%\subsection{Copper Indium Gallium Selenide} 
\gls{cigs} (\ch{CuIn_{x}Ga_{1-x}Se2}) is of the chalcopyrite (\ch{CuFeS2}) group (tetragonal crystal system). 
%It was 
\ch{CuInSe2} and \ch{CuGaSe2} were first synthesised in 1953 by Harry Hahn et al.\cite{hahn1953untersuchungen}.
The potential use of \ch{CuInSe2} as \gls{pv} material in combination with \ch{CdS} was first mentioned in 1974\cite{wagner1974cuinse2}.
%Already in 1975 efficiencies of cells of over 10\% were achieved.\cite{kazmerski1976thin}
Cells with efficiencies of over 10\% were achieved already by 1975\cite{kazmerski1976thin}.
Today, 
\gls{cigs} modules (multiple \gls{pv} cells in series) 
reach efficiencies of up to 16\%\cite{feurer2017cigs},
monocrystalline silicon \gls{pv} modules reach efficiencies of 14-20\%
and polycrystalline silicon \gls{pv} modules 12-17\%\cite{mcevoy2011practical}.

Just like CdTe, GaAs and amorphous silicon, CIGS has much higher absorption coefficients 
(lower penetration depth) of visible light than crystalline silicon (see table \ref{tab:cigs:alpha}). 
This is due to a direct band gap rather than an indirect band gap (like crystalline silicon). 
These thin film \gls{pv}s not only use less material, but also can be used in flexible applications.

@@

Amazingly, the band gap of CIGS can be varied between \ev{1} and \ev{1.7} by varying the indium gallium ratio.
This is a result of the large difference of band gaps of \ch{CuInSe2} and \ch{CuGaSe2} (see table \ref{tab:cigs}). 
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In figure \ref{fig:cigs} the schematic layer sequence of a standard \gls{cigs} thin film cell is shown. 
Typically, a \um{1} thick molybdenum layer is deposited on soda lime glass. 
The sodium in the glass diffuses through the molybdenum layer and increases efficiency and reliability by directing the growth of \gls{cigs} in 112 direction\cite{hedstrom1993cigs}.
A \gls{cigs} layer of 1-\um{2} thickness is applied on top via co-evaporation from elemental sources controlled by a mass spectrometer\cite{hedstrom1993cigs}.
The p-type doping of \gls{cigs} is achieved by adding more than stoichiometric copper to the mix. 
The heterojunction is then completed by deposition of \ch{CdS} (typically \nm{50} thick).
\ch{CdS} was earlier used as front contact, but now only acts as n-type wide-gap window and buffer. 
\ch{ZnO} has a band gap of \ev{3.2} and is therefore transparent for visible light. 
The \ch{ZnO} window layer (usually of thickness 50-\nm{70} is highly conductive (especially the aluminium doped layer) and acts as front contact.

%
Instead of glass as substrate, steel and polymers (e.g. polyimide\cite{feurer2017cigs}) can be used to create flexible \gls{cigs} modules. 
They both come with their own inconveniences. 
Polymers generally have low thermal stability compared with ceramics and metals which restrict preparation temperatures of \gls{cigs}.
Steel, on the other hand, is temperature resistant enough, but is an electric conductor. 
The conductance of steel can be masked by a insulator layer (e.g. \ch{ZrO2}, \ch{Al2O3}).

@@

%\section{Materials and Their Analysis}
\section{Sample preparation}
%\todo{COATING OF THE SUBSTRATE or sample preparation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Properties of Zirconium oxide}
Zirconium oxide \gls{zro} is a ceramic with a band gap of 5-7 eV\cite{Anwar2017} and relative permittivity of circa 20 at room temperature\cite{kukli2001dielectric}. 
This makes it attractive as an insulator for semiconductor and \gls{pv} industry. 
It is monoclinic below 1050 °C, tetragonal between 1170 °C and 2370 °C, and cubic above 2370 °C\cite{Nielsen2005}.
The cubic phase can be stabilized down to room temperature by the addition of magnesia (\ch{MgO}), calcia (\ch{CaO}) or yttria (\ch{Y2O3}) which avoids mechanical failing due to shrinkage 
when cooling and undergoing phase transition\cite{Nielsen2005}.
It is very resistant to acids (except \ch{HF} and hot \gls{h2so4}) and alkalis\cite{Nielsen2005}.
%Hydrous Zirconium Oxide (\ch{Zr(OH)8 * 16 H2O}) gel can be produced by neutral hydrolysis of sodium zirconate (\ch{NaZrO3})\cite{Nielsen2005}.
%"Zirconium alkoxides hydrolyze quite easily, [providing] a route to high purity, high-surface-area zirconium oxide"\cite{Nielsen2005}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Sol-Gel and Doctor Blading}
\subsection{Tape Casting}
%\td{what is it? What is it used for? How does it work? What different kinds are there? }One of the advantages of sol-gel process is that it can be used in roll-to-roll procedures.
%
\Gls{db} (also known as tape casting) is widely used in the textile, paper, photographic film, printing and ceramic industries.
The roll-to-roll compatible process can fabricate highly uniform flat films over large areas\cite{yang2010large}.
A blade is moved over a substrate spreading a slurry at a fixed distance with a fixed velocity.
In roll-to-roll processes the substrate moves instead of the blade.

>>>>

%\td{https://en.wikipedia.org/wiki/Thesis}
%\ds{what is it? What is it used for? How does it work? What different kinds are there? }
%\ds{what? how? why?}
This chapter can be broken down into three sections. 
The first section tries to shine light on the evolution of PV and give some background information on \gls{cigs} absorber.
The next section concerns the description of materials and scientific methods used during the experminental part of this work. 
The third and last part focuses on the algorithmic, statistical and analytical methods used to optimize and predict material properties.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Photovoltaics}
%\subsection{Problems of current energy supply}
The world wide energy consumption has more than doubled between 1970 and 2015\cite{BP2017} 
and according to recent studies both fossil\cite{BGR2017} and uranium sources\cite{Uran2006} 
will be exhausted within the next 100 years. 
Even though this time period is not exact and highly dependent on detection methods of resources, 
the situation demands the fast 
development of sustainable energy sources. 
% this number is rather small and brings us in \textit{zugzwang} to develop sustainable energy sources. 
One viable option is \gls{pv}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{History of Photovoltaics}
The photoelectric effect was first described in 1839 by french scientist Alexandre 
Edmond \linebreak[4] 
Becquerel\cite{becquerel1839memoire}. %, the father of Henri Becquerel (the person after whom the unit is named).
Another relevant piece in the \gls{pv} jigsaw was brought to light
%discovered
with the discovery of photo conductivity of selenium
by British engineer Willouhgby Smith\cite{Smith1873Selenium}.
In 1876 William Adams and Richard Day\cite{Adams1876Selenium} showed that 
the energy of light can be directly converted into electrical energy by a bar of 
selenium with attached platinum electrodes.
And finally, in 1905 Einstein described the physical background of the photoelectric 
effect with his light quantum theory\cite{einstein1905erzeugung}.
%\todo{https://doi.org/10.1063/1.1716492}
In the late 1950s the first solar cells (with power conversion efficiencies around 10 percent\cite{prince1958}) were used in niche applications such as space exploration.  
In 1958 the US American Vanguard I\cite{vanguard2004} and the soviet Sputnik III\cite{sputnik1959} were the first satellites with solar cells.
These "solar batteries" - as they were called then - allowed the transmission system of Vanguard I to be operating for over a year after the chemical battery powered system stopped transmitting after 20 days\cite{vanguard2004}. 
%
Eventually, the interest in photovoltaic and other alternative energy sources 
rose - fuelled by the oil crisis in 1973 - 
and the development of photovoltaic devices for the consumer market was boosted. 
This development lead to a drop in 
average price for \gls{pv} module from \$ 100 per watt in 1975 
%to \$ 4 per watt in 2007\cite{pagliaro2008flexible}. 
to under \$ 1 per watt in 2022\cite{irena2023renewable}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Photovoltaics Basics}
The process of conversion of photons into electric energy can be broken down into two essential steps: 
the generation of an electron-hole pair through photon absorption, the electron-hole separation by the built in electric field at the p-n junction and finally collection of the electrons and holes at the opposite terminals of the device\cite{markvart2013principles}.
This means that \gls{pv} cells are basically diodes, which have a low resistance in one direction and a high resistance in the other direction. 
%This is often achieved through a p-n junction.
The n-type side of the p-n junction has excess electrons and p-type side has excess electron holes. 
If the n- and p-type are of the same basis material, they are called homojunctions (e.g. silicon); if not, heterojunctions (e.g. \ch{CdS}/\gls{cigs} and \ch{CdS/CdTe})\cite{breitenstein2013understanding}.
%
The first marketable \gls{pv} were crystalline silicon photovoltaic modules which still 
have the biggest market share in the \gls{pv} segment (including polycrystalline and monocrystalline silicon).
In 2022 over 88\% of all sold \gls{pv} where made of silicon (including amorphous silicon)\cite{breitenstein2013understanding}.
%
A comprehensive overview on different \gls{pv} technologies can be found in \cite{markvart2013principles}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Copper Indium Gallium Selenide Solar Cell}
%\subsection{Copper Indium Gallium Selenide} 
\gls{cigs} (\ch{CuIn_{x}Ga_{1-x}Se2}) is of the chalcopyrite (\ch{CuFeS2}) group (tetragonal crystal system). 
%It was 
\ch{CuInSe2} and \ch{CuGaSe2} were first synthesised in 1953 by Harry Hahn et al.\cite{hahn1953untersuchungen}.
The potential use of \ch{CuInSe2} as \gls{pv} material in combination with \ch{CdS} was first mentioned in 1974\cite{wagner1974cuinse2}.
%Already in 1975 efficiencies of cells of over 10\% were achieved.\cite{kazmerski1976thin}
Cells with efficiencies of over 10\% were achieved already by 1975\cite{kazmerski1976thin}.
Today, 
\gls{cigs} (multiple \gls{pv} cells in series) 
reach efficiencies of up to 19\%,
monocrystalline silicon \gls{pv} modules reach efficiencies of 24\%
and polycrystalline silicon \gls{pv} modules 20\%\cite{green2023solar}.

Just like CdTe, GaAs and amorphous silicon solar cells, CIGS has much higher absorption coefficients of UV, visible and IR light than crystalline silicon (see table \ref{tab:cigs:alpha}). 
This is due to a direct band gap rather than an indirect band gap (like crystalline silicon). 
These thin film \gls{pv}s not only use less material, but also can be used in flexible applications.

@@

The band gap of CIGS can be varied between \ev{1} and \ev{1.7} by varying the indium-gallium and sulfur-selenium ratios.
This is a result of the large difference of band gaps of \ch{CuInSe2} and \ch{CuGaSe2} (see table \ref{tab:cigs}). 
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In figure \ref{fig:cigs} the schematic layer sequence of a standard \gls{cigs} thin film cell is shown. 
Typically, a \um{1} thick molybdenum layer is deposited on soda lime glass. 
The sodium in the glass diffuses through the molybdenum layer and increases efficiency and reliability by directing the growth of \gls{cigs} in the 112 direction\cite{hedstrom1993cigs}.
A \gls{cigs} layer of 1-\um{2} thickness is applied on top via co-evaporation from elemental sources\cite{hedstrom1993cigs}.
The p-type doping of \gls{cigs} is achieved by adding more than stoichiometric copper to the mix. 
The heterojunction is then completed by deposition of \ch{CdS} n-type layer (typically \nm{50} thick).
\ch{CdS} was earlier used as front contact, but now only acts as n-type wide-gap window and buffer. 
After the \ch{CdS} layer 
A window layer of intrinsic \ch{ZnO} is deposited after the \ch{CdS}, followed by a highly conductive aluminium doped layer. 
\ch{ZnO} has a band gap of \ev{3.2} and is therefore transparent for visible light. 
The \ch{ZnO} window layer (usually of thickness 50-\nm{70} is highly conductive (especially the aluminium doped layer) and acts as front contact.

%
Instead of glass as substrate, steel and polymers (e.g. polyimide\cite{feurer2017cigs}) can be used to create flexible \gls{cigs} modules. 
They both come with their own inconveniences. 
Polymers generally have low thermal stability compared with ceramics and metals which restrict the fabrication temperature of \gls{cigs}.
Steel, on the other hand, is temperature resistant enough, but is an electric conductor, which is problematic for the serial interconnection of cells into modules. 
Thus, an insulating layer has to be deposited on the steel substrate. 
%The conductance of steel can be masked by a insulator layer (e.g. \ch{ZrO2}, \ch{Al2O3}).

@@

%\section{Materials and Their Analysis}
\section{Sample preparation}
%\todo{COATING OF THE SUBSTRATE or sample preparation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Properties of Zirconium oxide}
Zirconium oxide \gls{zro} is a ceramic with a band gap of 5-7 eV\cite{Anwar2017} and relative permittivity of circa 20 at room temperature\cite{kukli2001dielectric}. 
This makes it attractive as an insulator for semiconductor and \gls{pv} industry. 
It is monoclinic below 1050 °C, tetragonal between 1170 °C and 2370 °C, and cubic above 2370 °C\cite{Nielsen2005}.
The cubic phase can be stabilized down to room temperature by the addition of magnesia (\ch{MgO}), calcia (\ch{CaO}) or yttria (\ch{Y2O3}). 
This prevents mechanical failing due to shrinkage 
when cooling and undergoing phase transition\cite{Nielsen2005}.
\ch{ZrO2} is very resistant to acids (except \ch{HF} and hot \gls{h2so4}) and bases\cite{Nielsen2005}.
%Hydrous Zirconium Oxide (\ch{Zr(OH)8 * 16 H2O}) gel can be produced by neutral hydrolysis of sodium zirconate (\ch{NaZrO3})\cite{Nielsen2005}.
%"Zirconium alkoxides hydrolyze quite easily, [providing] a route to high purity, high-surface-area zirconium oxide"\cite{Nielsen2005}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Sol-Gel and Doctor Blading}
\subsection{Tape Casting}
%\td{what is it? What is it used for? How does it work? What different kinds are there? }One of the advantages of sol-gel process is that it can be used in roll-to-roll procedures.
%
Tape casting (also known as tape casting) is widely used in the textile, paper, photographic film, printing and ceramic industries.
The roll-to-roll compatible process gives rise to highly uniform films over large areas\cite{yang2010large}.
A blade is moved over a substrate spreading a slurry at a fixed distance with a fixed speed.
In roll-to-roll processes the substrate moves instead of the blade.
